### 2015-10-10 manuscript/content/related.tex
Added proper style files, pages are now numbered in accordance with format.
Small revisions to Introduction and Related Work sections.

\section{Related Work}
There are a few ways of approaching the problem of determining a person's blood alcohol content. One approach is to model mathematically the elimination of ethanol in the human body. In this case, the Widmark equation, published in 1932 by E.M.P. Widmark, is a very popular one, \begin{equation}
•C=\frac{A}{rW}-(\beta t)
\end{equation} where $C$ is the BAC, $r$ and $\beta$ are empirically determined constants, $A$ is the mass of the consumed alcohol, and $W$ is the body weight of the person.
	These days, there have been several improvements and variants. Douglas Posey and Ashraf Mozayani published an excellent article comparing this model using parameters determined by different researchers and discussing different models \cite{Posey:2007}. They found that the Widmark equation tends to overestimate, and that there can be significant discrepancy between the results of the different models. Despite that, they do provide a rough estimate. The problem is that these models also require a good deal of information that prohibit their use in a non-intrusive, drunkenness warning system.

Another approach to the problem is simply to measure the BAC directly. Transdermal ethanol sensors have been a recent option for this approach. These can provide a discreet way to measure intoxication, but they are accompanied by the problem of a significant time lag between the sensed alcohol concentration and actual blood alcohol concentration. Gregory D. Webster and Hampton C. Gabler closely investigated this problem. They found that the lag is predictable, but not constant, and requires additional information about the drinks taken to accurately predict \cite{Webster:2007}.

>>>>

\section{Related Work}
There are a few ways of approaching the problem of determining a person's blood alcohol content. One approach is to devise a mathematical model of the elimination of ethanol in the human body. In this case, the Widmark equation, published in 1932 by E.M.P. Widmark, is a very popular one; \begin{equation}C=\frac{A}{rW}-(\beta t) \enspace ,
\end{equation} where $C$ is the BAC, $r$ and $\beta$ are empirically determined constants, $A$ is the mass of the consumed alcohol, and $W$ is the body weight of the person. These days, there have been several improvements and variants. Douglas Posey and Ashraf Mozayani published an excellent article comparing this model using parameters determined by different researchers and discussing different models \cite{Posey:2007}. They found that the Widmark equation tends to overestimate, and that there can be significant discrepancy between the results of the different models. Despite that, they do provide a rough estimate. The problem is that these models also require a good deal of information that prohibit their use in a non-intrusive, drunkenness warning system.

Another approach to the problem is simply to measure the BAC directly. Transdermal ethanol sensors have been a recent option for this approach. These can provide a discreet way to measure intoxication, but they are accompanied by the problem of a significant time lag between the sensed alcohol concentration and actual blood alcohol concentration. Gregory D. Webster and Hampton C. Gabler closely investigated this problem. They found that the lag is predictable, but not constant, and requires additional information about the number of drinks taken by the user to accurately predict it \cite{Webster:2007}.
